signalHsmm with k-mer hidden states

### 2015-06-22 signalHSMM_kMer_report.Rmd
adding duration estimated with kernel density estimator

First let us load data
```{r, cache=TRUE}
other_soft <- read.csv2("benchmark_other_new.csv")

@@

signalHsmm2010 <- train_hsmm(read_uniprot("sp1950_2010.txt", euk = TRUE, what = "signal"), 
                             aa_group = group_best)
signalHsmm1989 <- train_hsmm(read_uniprot("sp1950_1989.txt", euk = TRUE, what = "signal"), 
                             aa_group = group_best)
signalHSMM_proteins <- read_uniprot("sp1950_2010.txt", euk = TRUE, what = "signal")
benchmark_full <- read_uniprot("sp2010_2015.txt", euk = TRUE, what = "signal")
benchmark_data <- read.fasta("benchmark_data.fasta", seqtype = "AA")
benchmark_data2 <- lapply(c(benchmark_full,benchmark_data[-c(1:218)]), function(i) i[1L:ifelse(length(i) > 80, 80, length(i))])

@@

>>>>

First let us load data
```{r, cache=TRUE}
other_soft <- read.csv2("benchmark_other.csv")

@@

signalHsmm2010 <- train_hsmm(read_uniprot("sp1950_2010.txt", euk = TRUE, what = "signal"), 
                             aa_group = group_best)
signalHsmm1989 <- train_hsmm(read_uniprot("sp1950_1989.txt", euk = TRUE, what = "signal"), 
                             aa_group = group_best)
signalHSMM_proteins <- read_uniprot("sp1950_2010.txt", euk = TRUE, what = "signal")
benchmark_full <- read_uniprot("sp2010_2015.txt", euk = TRUE, what = "signal")
benchmark_data <- read.fasta("benchmark_data.fasta", seqtype = "AA")
benchmark_data2 <- lapply(c(benchmark_full,benchmark_data[-c(1:214)]), function(i) i[1L:ifelse(length(i) > 80, 80, length(i))])

@@

Now, what happens when we use kernel density estimation?
```{r}
params = structure(c(0.00345173057742305216, 0.16303340280710845733, 0.18328936325298567089, 0.32191072063759601507, 0.12710730373689624328, 0.19479707117476749434, 0.07149501410718961392, 0.05102665325739586671, 0.02061953603483871952, 0.01232173478541280856, 0.00339291179532653139, 0.00314522392528060902, 0.00050543218629833602, 0.00000944936698432368, 0.00000000009143740374, 0.00000000000000000000, 0.00000000000000000004, 0.00000000000000000321, 0.00000000000000000290, 0.00000000000000000501, 0.00000000000000000835, 0.00000000000000000088, 0.00000000000000000146, 0.00000000000000000000, 0.00000000000000000592, 0.00000000000000000000, 0.00000000000000000345, 0.00000000000000000036, 0.00000000000000000132, 0.00000000000000000276, 0.00000000000000000001, 0.00000000000000000462, 0.00119575265523844728, 0.00135312474054827118, 0.00278142092346731536, 0.00184134527771419310, 0.00400555470679759759, 0.01737188174042058122, 0.04070639179659169687, 0.06492241958211328323, 0.10486627831232180064, 0.13185802303839422311, 0.16522286797419358240, 0.14092085504016543807, 0.13473723690401800956, 0.08898241528270439682, 0.05443355717845509839, 0.04403282913502165608, 0.02561338612799781561, 0.01320007003819387639, 0.01069067991482806901, 0.00517725596697340799, 0.00181848832708673882, 0.00093206572991894022, 0.00156817541687766086, 0.00051169053398325657, 0.00077312532731958154, 0.00004559742198773287, 0.00000001037808743568, 0.00000000000000871706, 0.00000000000000000000, 0.00000000000000000000, 0.00000000000000000000, 0.00000000000000000000, 0.00345173057742305216, 0.16303340280710845733, 0.18328936325298567089, 0.32191072063759601507, 0.12710730373689624328, 0.19479707117476749434, 0.07149501410718961392, 0.05102665325739586671, 0.02061953603483871952, 0.01232173478541280856, 0.00339291179532653139, 0.00314522392528060902, 0.00050543218629833602, 0.00000944936698432368, 0.00000000009143740374, 0.00000000000000000000, 0.00000000000000000004, 0.00000000000000000321, 0.00000000000000000290, 0.00000000000000000501, 0.00000000000000000835, 0.00000000000000000088, 0.00000000000000000146, 0.00000000000000000000, 0.00000000000000000592, 0.00000000000000000000, 0.00000000000000000345, 0.00000000000000000036, 0.00000000000000000132, 0.00000000000000000276, 0.00000000000000000001, 0.00000000000000000462, 0.03125, 0.03125, 0.03125,
0.03125, 0.03125, 0.03125, 0.03125, 0.03125, 0.03125, 0.03125,
0.03125, 0.03125, 0.03125, 0.03125, 0.03125, 0.03125, 0.03125,
0.03125, 0.03125, 0.03125, 0.03125, 0.03125, 0.03125, 0.03125,
0.03125, 0.03125, 0.03125, 0.03125, 0.03125, 0.03125, 0.03125,
0.03125), .Dim = c(32L, 4L),
.Dimnames = list(NULL, c("n", "h","c", "")))

  parametersSet2 <- add_k_mer_state2(kMer1, signalHsmm2010$pipar, signalHsmm2010$tpmpar, signalHsmm2010$od, 
                                     params, pState1, nState1, pTrans1, d=3)
  parametersSet3 <- add_k_mer_state2(kMer2, pipar = parametersSet2$pipar, tpmpar = parametersSet2$tpmpar, 
                                     od = parametersSet2$od, params = parametersSet2$params,
                                     pState2, nState2, pTrans2, d=3)
  parametersSet4 <- add_k_mer_state2(kMer3, pipar = parametersSet3$pipar, tpmpar = parametersSet3$tpmpar, 
                                     od = parametersSet3$od, params = parametersSet3$params, 
                                     pState3, nState3, pTrans3, d=3)
  parametersSet5 <- add_k_mer_state2(kMer4, pipar = parametersSet4$pipar, tpmpar = parametersSet4$tpmpar, 
                                     od = parametersSet4$od, params = parametersSet4$params, 
                                     pState4, nState4, pTrans4, d=3)
  overall_probs_log <- signalHsmm2010$overall_probs_log
  maxSignal <- 45
```
